---
title: "Approximating Central Area from Multiple Addresses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
libraries <- c("data.table", "tidyverse", "lubridate", "leaflet")
lapply(libraries, require, character.only = T)
```

## Scroll Down Innit


```{r map innit}
#datatable
coord <- data.frame(name = c("American Chutiya Chaamp Panchod Lund",
                             "Chutiya Chaamp Panchod Lund",
                             "Nandos Panchod Ben ki Bundi",
                             "Opioid Pandamic Panchod ki Pendu",
                             "Me"),
                    lat = c(43.9398,
                            43.89892,
                            43.76061,
                            43.92319,
                            43.76966),
                    long = c(-78.8734,
                             -79.22495,
                             -79.39854,
                             -79.45457,
                             -79.37008))

x1 <- min(coord$lat) %% 1
x2 <- max(coord$lat) %% 1

y2 <- max(abs(coord$long)) %% 1

central.lat <- min(coord$lat) + (x1 + ((x2 - x1)/2))
central.long <- abs(floor(max(coord$long))) + ((y2)/2) 

restaurants_near <- paste0("https://www.google.ca/maps/search/Restaurants/@",
                           43.87021, ",",
                           -79.22728, 
                           ",13z")

#map
leaflet(coord) %>%
        addProviderTiles(providers$CartoDB.Positron) %>%
        addMarkers(lat = ~lat,
                   lng = ~long,
                   popup = ~name) %>%
        addCircles(weight = 1,
                   radius = 5e3,
                   lat = 43.87021,
                   lng = -79.22728,
                   popup = "THIS IS ABOUT CENTRAL<br>NOW FIND A VENUE <a href='https://www.google.ca/maps/search/Restaurants/@43.87021,-79.22728,13z'>HERE</a> INNIT")